\Title

### 2015-11-02 manuscript.tex
Finished estimation of zref and density contrast

>>>>

The depth of the Normal Earth Moho ($z_{ref}$)
and the density-contrast of the anomalous Moho ($\Delta\rho$)
are other hyper-parameters of the inversion.
That is, their value influences the final solution
but they are not estimated during the inversion.
Both hyper-parameters cannot be determined from the gravity data alone.
Estimating $z_{ref}$ and $\Delta\rho$ requires
information that is independent of the gravity data,
such as knowledge of the parameters at certain points.
This information can be used in a manner similar to
the cross-validation described in the previous section.
In this study, we use point estimates of the Moho depth
to determine the optimal values of $z_{ref}$ and $\Delta\rho$.
These points will generally come from seismologic studies,
like receiver functions, surface wave dispersion, and deep refraction
experiments.

Let $\mathbf{z}_s^o$ be a vector of $N_s$ known Moho depths.
We use the mean square error (MSE)
as a measure of how well a given inversion output $\mathbf{\hat{p}}^k$
fits the know depths.
The optimal values of $z_{ref}$ and $\Delta\rho$
are the ones that best fit the independent known Moho depths
(i.e., produce the smallest MSE).
However, the points do not necessarily coincide
with the model elements of the inversion.
Before computing the MSE,
we interpolate $\mathbf{\hat{p}}^k$ on the known points
to obtain the predicted depths $\mathbf{z}_s^k$.
The MSE is defined as

\begin{equation}
    MSE = \dfrac{\|\mathbf{z}^o_s - \mathbf{z}^k_{s}\|^2}{N_s}.
    \label{eq:msehyper}
\end{equation}

The algorithm for estimating $z_{ref}$ and $\Delta\rho$ is:

\begin{enumerate}
    \item For each combination of
        $z_{ref,l} \in [z_{ref,1},z_{ref,2},\ldots,z_{ref,N_z}]$ and
        $\Delta\rho_m \in
         [\Delta\rho_1,\Delta\rho_2,\ldots,\Delta\rho_{N_{\rho}}]$:
    \begin{enumerate}
        \item Perform the inversion on the training data set
            $\mathbf{d}^o_{inv}$ using $z_{ref,l}$, $\Delta\rho_m$, and
            the previously estimated value of $\mu$.
            The inversion output is the vector $\mathbf{\hat{p}}^{l,m}$.
        \item Interpolate $\mathbf{\hat{p}}^{l,m}$
            on the known points to obtain the predicted depths
            $\mathbf{z}_s^{l,m}$.
        \item Calculate the MSE between $\mathbf{z}_s^o$ and
            $\mathbf{z}_s^{l,m}$ using Eq.~\ref{eq:msehyper}.
    \end{enumerate}
    \item The final solution is the $\mathbf{\hat{p}}^{l,m}$ corresponding to
        the smallest MSE.
\end{enumerate}

A similar approach was used by \citet{martins2010}
to estimate the parameters defining
the density-contrast variation with depth
of a sedimentary basin.
\citet{vandermeijde2013} also had
a similar methodology for dealing with the hyper-parameters,
though in a less formalized way.
